---
title: "Coursera Data Science Capstone Final Project"
author: "Harikrishna Vemula"
date: "05/06/2021"
output:
  ioslides_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  slidy_presentation: default
mode: selfcontained
job: Next Word Prediction
subtitle: By refering SwiftKey Data
highlighter: highlight.js
widgets: bootstrap
---



## Intial Note ##

**Introduction**

This is Coursera's Data Science Capstone Final Project Assignment.
This project utilizing SwiftKey's data along with open source provider www.bannedwordslist.com.
We can notice how we can model/train the data with basic mining concepts for get the accurate output through the code. I am proving reference urls in Reference section of this shiny presentation for your review.

**Objective**

When we type a phrase in the input box, we need to get a prediction of a single word after pressing submit.

## Modeling ##

**Prediction Model**

The prediction model describes following mining Key models items:

1) Data loading, read data and create data frames
2) Data Sampling 
3) Data Cleaning
4) Build N-Gram Tokenizer
5) Separate words and store into respective Ngrams
6) Save separated Ngrams into Physical folder 

**Next Word Prediction Shiny Web App**

Next word prediction shiny web app UI having following fields. 

1) Title
2) Input text box to enter word or phrase
3) output section which uses to display the predicted word from the mining model.Key Features:
4) Side panel and notification text for user experience.

## ##
**Algorithm**

Server code:
```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}

ngrams <- function(input_text){
  # Create a dataframe
  input_text <- data_frame(text = input_text)
  # Clean the Inpput
  replace_reg <- "[^[:alpha:][:space:]]*"
  input_text <- input_text %>%
    mutate(text = str_replace_all(text, replace_reg, ""))
  # Find word count, separate words, lower case
  input_count <- str_count(input_text, boundary("word"))
  input_words <- unlist(str_split(input_text, boundary("word")))
  input_words <- tolower(input_words)
  # Call the matching functions
  nextWord <- ifelse(input_count == 0, "Please enter a word to be guess what the next word should be.",
               ifelse (input_count == 1, bigram(input_words),
               ifelse (input_count == 2, trigram(input_words),
               ifelse (input_count == 3, quadgram(input_words)
               ))))
  if(nextWord == "?"){
    nextWord = "Unbale to predict the next word based on your input due to data related queries. Please try with aother word." 
  }
  return(nextWord)
}
```

UI code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
shinyUI(fluidPage(
  
  # Application title
  titlePanel("Next Word Prediction"),
  
  sidebarPanel(
    textInput("inputString", "Please enter a word",value = ""),
    submitButton('Submit'),
    br(),
    br(),
    br(),
    br()
  ),
  
  mainPanel(
    h4("Your Next Word should be : "),
    verbatimTextOutput("prediction")
   
  )
))
```


## References##

1) Source code GitHub Url

https://github.com/HarikrishnaVemula/Coursera_Datascience_CapstoneFinalProject

2) SwiftKey Data Source

https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip

3) Swear Words 

http://www.bannedwordlist.com/lists/swearWords.csv


